\subsection{Introduction to TCC Automation}
\begin{frame}{TCC Automation} 
\begin{block}{Introduction of TCC Automation}
Automation is the use of control systems and information technologies to reduce the need for human work in the production of goods and services. Raw data storage, electronic transfer, and the management of electronic business information comprise the basic activities of an office automation system.
\end{block}
\end{frame}
\newpage
\subsection{its Objective}
\begin{frame}{TCC Automation} 
\begin{block}{Objectives of TCC Automation}
\begin{itemize}
\item<2-> Make your work less tedious.
\item<3-> Trim hours off your workload.
\item<4-> Reduce repetitive keyboard strokes or mouse-clicks.
\item<5-> Make data entry easier with fewer tabs or mouse movements.
\item<6-> Take any job you do longhand and make the computer do it for you.
\end{itemize}
\end{block}
\end{frame}
\newpage
\subsection{Languages and tools used}
\begin{frame}{TCC Automation}
\begin{block}{Languages and tools used}
\begin{description}
\item[Programming language] : Python
\item[Framework] : Django
\item[Web Languages] : Html, Java Script, CSS
\item[Database] : Mysql
\end{description}
\end{block}
\end{frame}
\newpage
\begin{frame}{Python}
\begin{block}{About Python}
 Python is a dynamic language, as in python coding is very easy and also it require less coding and about its interpreted nature it is just exellent.Python is a high level programming language and Django which is a web development framework is written in python language.\\
Python is an easy to learn, powerful programming language.Python runs on Windows, Linux/Unix, Mac OS X.Python is free to use, even for commercial products.Python can also be used as an extension language for existing modules and applications that need a programmable interface.\\
\end{block}
\end{frame}
\newpage

\begin{frame}{Django}
\begin{block}{Django}
\Django Django is an open source web application framework written in python. It lets you build high-performing, elegant Web applications quickly. Django focuses on automating as much as possible. Django adopts the standard MVC(Model-View-Controller) design pattern. But instead, their naming convention is the MTV(Model-Template-View).\\

\end{block}
\end{frame}
\newpage
\begin{frame}{Django}
\begin{block}{MTV}
\begin{description}
\item[Model] is an object relational mapping to your database schema. So each model is a class which represent a table in your database.
\item[Template] is simply HTML for your views. It also allows you to display different messages depending on whether or not a user logged in.
\item[View] could be a homepage or a page to display a user's information, for instance
\end{description}
\end{block}
\end{frame}
\newpage
\begin{frame}{MySql}
\begin{block}{MySql}
Although Django supports all the Databases like sqlite, Mysql, postgresql etc but I used the Mysql. Mysql is world’s most popular open source database. MySQL is written in C and C++. Free-software-open source projects that require a full-featured database management system often use MySQL.\\
         One of the greatest advantage of Django is that it synchronises the database only with one command without having any need to send different queries for insertion, deletion, updation etc. There is a file named models.py which is used for purpose of creating database.The command used for database synchronisation is \\
\begin{center}        \$ python manage.py sycdb 
\end{center}

\end{block}
\end{frame}
\newpage
\subsection{My project}
\begin{frame}{TCC Automation}
\begin{block}{Report}
\begin{itemize}
\item<2->Suspense Report
\item<3->Suspense-Clearance Report
\item<4->T.A./D.A. Bill
\item<5->Performa Bill
\item<6->Job Register
\item<7->Yearly/Monthly Income Report
\item<8->Transport Bill
\item<9->Other charge Bill
\item<10->Faculty Income distribution
\end{itemize}
\end{block}
\end{frame}
\newpage
\begin{frame}{TCC Automation}
\begin{block}{Reports}
\begin{itemize}
\item<2->Main Register
\item<3->Receipt
\item<4->Department/lab Report
\item<5->Govt./Semi-Govt./Private Report
\item<6->Clearance Report
\item<7->General Bill
\end{itemize}
\end{block}
\end{frame}
\newpage
\subsection{Distribution of money}
\begin{frame}{TCC Automation}
\begin{block}{Distribution of money}
\begin{itemize}
\item<2->College Income
\item<3->Administrative
\item<4->Development Funds
\item<5->Consultatancy Asst.
\item<6->Service Tax
\item<7->Education Tax
\item<8->Higher-Education Tax
\end{itemize}
\end{block}
\end{frame}

